### 2013-01-26 mcmc.tex
title and acks

\newcommand{\this}{Introduction to Markov chain Monte Carlo}
\include{styles/dar}

@@

\thispagestyle{plain}\raggedbottom
\section*{Data analysis recipes:\ \this\footnotemark}

\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2010 by the authors. This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank\ldots
    }.
}

>>>>

\newcommand{\this}{Using Markov Chain Monte Carlo}
\include{styles/dar}

@@

\thispagestyle{plain}\raggedbottom
\section*{Data analysis recipes:\\ \this\footnotemark}

\footnotetext{%
    The notes begin on page~\pageref{note:first}, including the
    license\note{\label{note:first}
        Copyright 2010 by the authors. This work is licensed under a
        \href{http://creativecommons.org/licenses/by-nc-nd/3.0/deed.en\_US}{%
            Creative Commons Attribution-NonCommercial-NoDerivs 3.0 Unported
            License}.}
    and the acknowledgements\note{%
        We would like to thank
          Jo Bovy (IAS),
          Brendon Brewer (Auckland),
          Jonathan Goodman (NYU),
          Dustin Lang (CMU),
          \ldots
        for valuable advice and comments.}.
}
